A Sound Deep Embedding of Arbitrary Normal Modal Logics in Coq

### 2022-09-05 paper/paper.tex
Remove grant number (but why?)

\begin{acks}
  The present work was supported by Fundação de Amparo à Pesquisa de Minas
  Gerais (FAPEMIG) under grant APQ-01683-21 and Fundação de Amparo à Pesquisa de
  Santa Catarina (FAPESC) under grant 2021TR961.
\end{acks}

>>>>

\begin{acks}
  The present work was supported by Fundação de Amparo à Pesquisa de Minas
  Gerais (FAPEMIG) under grant APQ-01683-21 and Fundação de Amparo à Pesquisa de
  Santa Catarina (FAPESC). %under grant 2021TR961.
\end{acks}
